\texttt{MSnbase}, efficient and elegant R-based processing and visualisation of raw mass spectrometry data

### 2020-05-07 msnbase2.Rnw
add specs - closes #5
fix: number of processors
fix typo in code

\begin{figure}[p]
  \centering
<<plot_bench>>=
(p_read + p_sz + p_filt) / p_access + 
    plot_layout(heights = c(1, 0.75)) + 
    plot_annotation(tag_levels = 'a') &
    theme(axis.title = element_text(size = 10))
@
\caption{(a) Reading time (in seconds) and (b) data size in memory (in
  MB) to read/store 1, 5 and 10 files containing 1431 MS1 (on-disk
  only) and 6103 MS2 (on-disk and in-memory) spectra. (c) Filtering
  benchmark assessed over 10 interactions on in-memory and on-disk data
  containing 6103 MS2 spectra.  (d) Access time to spectra for the
  in-memory (left) and on-disk (right) backends for 1, 10, 100 1000,
  5000 and all 6103 spectra. On-disk backend: blue. In-memory backend:
  red. }
\label{fig:bench}
\end{figure}

@@

<<bc1, echo=TRUE, eval=FALSE>>=
bc <- readMSData("boxcar.mzML", mode = "onDisk") %>%
      bc_groups() %>%       ## identify BoxCar groups (bc_groups)
      filterBoxCar() %>%    ## keep only BoxCar spectra
      bc_zero_out_box() %>% ## remove signal outside of BoxCar segments
      combineSpectra(fcol = "bc_groups", ## reconstruct full spectrum
                     method = boxcarCompbine)
@

>>>>

\begin{figure}[p]
  \centering
<<plot_bench>>=
(p_read + p_sz + p_filt) / p_access + 
    plot_layout(heights = c(1, 0.75)) + 
    plot_annotation(tag_levels = 'a') &
    theme(axis.title = element_text(size = 10))
@
\caption{(a) Reading time (in seconds) and (b) data size in memory (in
  MB) to read/store 1, 5 and 10 files containing 1431 MS1 (on-disk
  only) and 6103 MS2 (on-disk and in-memory) spectra. (c) Filtering
  benchmark assessed over 10 interactions on in-memory and on-disk
  data containing 6103 MS2 spectra.  (d) Access time to spectra for
  the in-memory (left) and on-disk (right) backends for 1, 10, 100
  1000, 5000 and all 6103 spectra. On-disk backend: blue. In-memory
  backend: red. Benchmarks were performed on a Dell XPS laptop with an
  Intel i5-8250U processor 1.60 GHz (4 cores, 8 threads) and 7.5 GiB RAM
  running Ubuntu 18.04.4 LTS 64-bit. }
\label{fig:bench}
\end{figure}

@@

<<bc1, echo=TRUE, eval=FALSE>>=
bc <- readMSData("boxcar.mzML", mode = "onDisk") %>%
      bc_groups() %>%       ## identify BoxCar groups (bc_groups)
      filterBoxCar() %>%    ## keep only BoxCar spectra
      bc_zero_out_box() %>% ## remove signal outside of BoxCar segments
      combineSpectra(fcol = "bc_groups", ## reconstruct full spectrum
                     method = boxcarCombine)
@
